Pancreatic endocrinogenesis

### 2024-08-01 nbs/tutorials/pancreas/results/pancreas.qmd
refactor(nbs): migrate results notebook to subdir
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Pancreatic endocrinogenesis
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

@@

(
    model1_postprocessing_inputs,
    model1_postprocessing_outputs,
) = get_remote_task_results(
    execution_id="pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a",
    task_id="f26c1pjy-0-dn1-0-dn3",
)

(
    model2_postprocessing_inputs,
    model2_postprocessing_outputs,
) = get_remote_task_results(
    execution_id="pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a",
    task_id="f26c1pjy-0-dn1-0-dn6",
)
```

>>>>

---
title: Pancreatic endocrinogenesis
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

@@

execution_id = "pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a"

(
    model1_postprocessing_inputs,
    model1_postprocessing_outputs,
) = get_remote_task_results(
    execution_id=execution_id,
    task_id="f26c1pjy-0-dn1-0-dn3",
)

(
    model2_postprocessing_inputs,
    model2_postprocessing_outputs,
) = get_remote_task_results(
    execution_id=execution_id,
    task_id="f26c1pjy-0-dn1-0-dn6",
)
```
